Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-06-22 bbbq_article.tex
EOD
Can predict peptides

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Strength of Influenza A}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Our evolutionary experiment depends on the strength of the dataset.
Here we do a back-on-the-envelope calculation to assess if the dataset
is strong enough.

\begin{itemize}
	\item Genome size: $\approx 1.3 \cdot 10^4$ bases
	\item Relative genome size compared to COVID-19: $\approx 0.4$ (as $\frac{1.3 \cdot 10^4}{3.0 \cdot 10^4}$)
	\item Full genome sets: $\approx 3.2 \cdot 10^4$ (Influenza A)
	\item Relative number of genome sets compared to COVID-19: $\approx 6.4$ as much (as $\frac{\approx 32 \cdot 10^3}{5 \cdot 10^3}$)
	\item Relative time to accumulate mutations: $\approx 12$ times longer (average age $\approx$ 4 year, before 2015, already 8k sequences)
	\item Relative chance of observing transitions: $\approx 30$ (as $0.4 \cdot 6.4 \cdot 12$)
	\item Expected number of observed TMH mutations in COVID-19 that cause a transition: $\approx 8$
	\item Expected number of observed TMH mutations that cause a transition: $\approx 240$ (as $8 \cdot 30$)
\end{itemize}

Conclusion: seems strong enough to us.

@@

>>>>

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{IC50s per haplotype}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Per MHC haplotype, we simulated random peptides and measured the
predicted IC50 using MHCnuggets. 
Here, we show the IC50 value per haplotype that
is used to determine if a peptide binds to the haplotype's MHC.

\begin{figure}[!htbp]
  \includegraphics[width=0.9\textwidth]{ic50s_per_haplotype/ic50s_per_haplotype.png}
  Predicted IC50s (in nM) per MHC-I haplotype
  \caption{
    \richel{Used randomly simulated polypeptides, results are real}
  }
  \label{fig:ic50s_per_haplotype}
\end{figure}
